\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-09-23 chapters/wcble.tex
Describe simulation method

\section{Results}
simulation study
equatin snr
\subsection{Data simulation}
To verify our approach, we simulated 32 channel \ac{eeg} data with standard
10-20 electrode positions using the \textttt{simulate_evoked} method of the
MNE (version 1.8)~\cite{Gramfort2013} software package.
\Ac{erps} were generated by projecting a source time course in a dipole in the
left hemisphere to the scalp electrodes using a boundary element method forward
model~\cite{Mosher1999} MNE's \texttt{fsaverage} source space and anatomy.
We refer to~\textcite{Gramfort2014} for implementation details.
Pink noise generated using an infinite impulse response filter with transfer
function $\frac{B(z)}{A(z)} = \frac{1}{1 -1z^{-1}+0.15z^-2}$.

figure
Three kinds of source time courses, gaussian, a
morlet wavelet and a sine wave, to study the algorithm's behavior for different
waveforms.
equations with parameters
full simulation fig for wavelet

For each source time course,
pink noise is generated at all sources? and projected to the scalp

>>>>

\section{Results}
simulation study

\subsection{Data simulation}
To verify our approach, we simulated 32 channel \ac{eeg} data with standard
10-20 electrode positions using the \texttt{simulate\_evoked} method of the
MNE (version 1.8)~\cite{Gramfort2013} software package.
\Acp{erp} were generated by projecting a source time course in a dipole in the
left hemisphere to the scalp electrodes using a boundary element method forward
model~\cite{Mosher1999} MNE's \texttt{fsaverage} source space and anatomy.
We refer to~\textcite{Gramfort2014} for implementation details.
Pink spatial and  temporal noise are then added.
Temporal noise is generated by passing gaussian noise through an infinite
impulse response filter with transfer function
$\frac{B(z)}{A(z)} = \frac{1}{1 -1z^{-1}+0.15z^{-2}}$.
For pink spatial noise, a noise covariance matrix is constructed from the
cosine distances between electrode positions and scaling the resulting spatial
frequencies by $1/f$.

Evoked potentials are simulated for three different source time course waveforms,
a gaussian, a morlet wavelet and a sinusoid pulse with variable latency,
defined by the following formulas:
\begin{equation}
  f_\text{gaussian}(t,l) = a
  \frac{1}{\varsigma\sqrt{2\pi}}e^{-\frac{1}{2}\frac{\left(t-l\right)^2}{\varsigma/2}}
\end{equation}
\begin{equation}
  f_\text{morlet}(t,l) = ae^{-\left(\frac{t-l}{\frac{c}{2\pi f}}\right)^2}
\end{equation}
\begin{equation}
  f_\text{sine}(t,l) =
  \begin{cases}
    a\sin\left(2\pi f\left(t-l\right)\right) & \text{if  $l-\frac{1}{2f} < t < l-\frac{1}{2f}$} \\
    0 & \text{otherwise}
  \end{cases}
\end{equation}
with time $t$, latency $l$, and amplitude $a=\num{1e{-7}}$V.
The standard deviation that determines the width gaussian $\varsigma=0.1s$.
For the morlet wavelet, the number of cycles $c=3$ and the frequency $f=4Hz$.
For the sine pulse, the frequency $f=4$
For each of these, 100 target epochs containing the waveform and noise and 100
non-target epochs containing only noise were simulated.
Additionally, the target epochs were jittered by setting the latency offset $l$
of each target epoch to a random latency drawn from a normal distribution with 0 mean and standard
deviations of respectively $\sigma=0.1,0.2,0.3$s.
The noise was also scaled at different 32  different noise levels, with the \ac{snr} of a
target epoch ranging from 0 to -31dB, with
\begin{equation}
  \text{SNR} = 10\log_{10}\frac{\text{var}f(t,0)}{\text{var}\left(\text{noise}\right)}
\end{equation}

figure
